Statically Typed String Sanitation Inside a Python

### 2014-08-19 sanitation-psp14/sanitation-psp14-short.tex
\cup -> +

The definition of \textsc{S-T-Case} is subtle because even simple string operations sometimes require complicated operations on regular expressions. Peeling off the first character of a string is deterministic -- the first character is always one, concrete value. However, a regular expression describing the first character of any matching string might recognize multiple concrete values. For instance, the first character of ``CMU" is always ``C"; however, if the expression associated with this string is CMU$\cup$KIT, then the expression describing the first character is C$\cup$K.
Therefore, an operation on languages corresponding to case analysis on strings must consider one-character prefixes (a head) and their corresponding suffixes (a tail).

@@

\begin{defn}[Definition of \lhead{r}]
The function $\lhead{r}$ is defined in terms of the structure of $r$:
\begin{itemize}
\item $\lhead{a r'} = a$ where $a \in \Sigma$
\item $\lhead{r_1 \cup  r_2}  = \lhead{r_1} \cup \lhead{r_2}$
\item $\lhead{r*} = \lhead{r}$
\item $\lhead{.} = a_1 \cup a_2 \cup ... \cup a_n$ for all $a_i \in \Sigma$ where $|\Sigma| = n$
\item $\lhead{\epsilon} = \epsilon$.
\end{itemize}
\end{defn}

@@

\begin{defn}[Definition of \ltail{r}]
The function \ltail{r} is defined in terms of $\lhead{r}$.
Note that $\lhead{r} = a_1 \cup a_2 \cup ... \cup a_i$.
We define $\ltail{r} = \delta_{a_1}(r) \cup \delta_{a_2}(r) \cup ... \cup \delta_{a_i}(r)$
where $\delta_s(r)$ is the Brzozowski derivative of $r$ with respect to $s$ \cite{bowzer}.
\end{defn}

>>>>

The definition of \textsc{S-T-Case} is subtle because even simple string operations sometimes require complicated operations on regular expressions. Peeling off the first character of a string is deterministic -- the first character is always one, concrete value. However, a regular expression describing the first character of any matching string might recognize multiple concrete values. For instance, the first character of ``CMU" is always ``C"; however, if the expression associated with this string is CMU$+$KIT, then the expression describing the first character is C$+$K.
Therefore, an operation on languages corresponding to case analysis on strings must consider one-character prefixes (a head) and their corresponding suffixes (a tail).

@@

\begin{defn}[Definition of \lhead{r}]
The function $\lhead{r}$ is defined in terms of the structure of $r$:
\begin{itemize}
\item $\lhead{a r'} = a$ where $a \in \Sigma$
\item $\lhead{r_1 +  r_2}  = \lhead{r_1} + \lhead{r_2}$
\item $\lhead{r*} = \lhead{r}$
\item $\lhead{.} = a_1 + a_2 + ... + a_n$ for all $a_i \in \Sigma$ where $|\Sigma| = n$
\item $\lhead{\epsilon} = \epsilon$.
\end{itemize}
\end{defn}

@@

\begin{defn}[Definition of \ltail{r}]
The function \ltail{r} is defined in terms of $\lhead{r}$.
Note that $\lhead{r} = a_1 + a_2 + ... + a_i$.
We define $\ltail{r} = \delta_{a_1}(r) + \delta_{a_2}(r) + ... + \delta_{a_i}(r)$
where $\delta_s(r)$ is the Brzozowski derivative of $r$ with respect to $s$ \cite{bowzer}.
\end{defn}
